Towards Practical First-Order Model Counting

### 2023-12-27 paper.tex
Some changes

@@

  $B \gets \emptyset$\;
  \ForEach{equation $(f(\mathbf{x}) = \expr{}) \in E$}{
    \ForEach{function call $g(\mathbf{y} - \mathbf{c}) \in \expr{}$}{\label{line:functioncall}
      \ForEach{$c_{i} \in \mathbf{c}$}{
        \For{$n \gets 0$ \KwTo $c_{i} - 1$}{\label{line:lim}
          $B \gets B \cup \{\, f(\mathbf{x})[x_{i}/n] \,\}$\;\label{line:insert}
          \lIf{$f \ne g$}{$B \gets B \cup \{\, g(\mathbf{y})[y_{i}/n] \,\}$}\label{line:signature}
        }
      }
    }
  }
\end{algorithm}

@@

>>>>

An important change to the compilation algorithm. We make the FCGs satisfy the
following property. For every domain $\Delta$, for every directed path $P$
without Ref nodes, the number of atom counting or (generalised) domain recursion
operations on $\Delta$ on $P$ is at most one.

@@

  $B \gets \emptyset$\;
  \ForEach{equation $(f(\mathbf{x}) = \expr{}) \in E$}{
    \ForEach{function call $f(\mathbf{x} - \mathbf{c}) \in \expr{}$}{\label{line:functioncall}
      \ForEach{$c_{i} \in \mathbf{c}$}{
        \For{$n \gets 0$ \KwTo $c_{i} - 1$}{\label{line:lim}
          $B \gets B \cup \{\, f(\mathbf{x})[x_{i}/n] \,\}$\;\label{line:insert}
        }
      }
    }
  }
\end{algorithm}

@@

TODO: I changed the algorithm

\begin{theorem}
  Under the following assumptions, \cref{alg1} is guaranteed to return a
  sufficient set of base cases:
  \begin{itemize}
    \item there is no mutual recursion (i.e., cyclic dependencies between
          functions);
    \item each function $f$ has exactly one equation with $f$ on the LHS;
    \item in the recursive definition of function $f(x_{1},\dots,x_{n})$, the
          $i$-th argument of each call to $f$ on the RHS is of the form
          $x_{i} - c_{i}$, where:
          \begin{itemize}
            \item $c_{i} \ge 0$ for all $i$, and
            \item $c_{i} > 0$ for at least one $i$.
          \end{itemize}
  \end{itemize}
\end{theorem}

\begin{example}
  For an equation $f(m, n) = 2 \times f(m-1, n)$, \cref{alg1} returns $f(0, n)$.
\end{example}

NOTE: function calls such as $f(n-m)$ and $f(n-m-1)$ are ignored.
